Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms_apj/ms.tex
1st sub to AAS Journal

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

\input{preamble}
\slugcomment{To be submitted to the ApJ}
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{document}
%{\tiny  \RevisionInfo}

@@

%=============================================================================
%                                Front matters
%==============================================================================

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to
%our understanding of the
%processes governing the formation and evolution of both the SMBHs and their host galaxies.
% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution.
% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
It is currently not well-understood when and how the supermassive black holes (SMBHs) and
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
but direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
spatially unresolved CO observations of 
a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
 \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

The \ncode{gildas} package was used to calibrate and analyze the visibility data.
The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is produced by averaging over 3.16\,GHz of line-free bandwidth. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
%
% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35% add in quad
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\subsection{VLA (Archival)}
Our analysis also uses archival data of the 4.885\,GHz %4.88510 GHz
radio continuum obtained with the
VLA (Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

>>>>

\usepackage[normalem]{ulem}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}}

\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{etoolbox}

\makeatletter

% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
{\@citea\NAT@hyper@{%
\NAT@nmfmt{\NAT@nm}%
\hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
\NAT@date}}
{\@citea\NAT@nmfmt{\NAT@nm}%
\NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}

% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
{\@citea\NAT@hyper@{%
\NAT@nmfmt{\NAT@nm}%
\hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
{\@citeb\@extra@b@citeb}%
\NAT@date}}
{\@citea\NAT@nmfmt{\NAT@nm}%
\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
{}{}

\makeatother
%
\usepackage{xspace}
%
\usepackage{apjfonts}
\usepackage{amssymb, amsmath} % for e.g. \lesssim
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros} % for understanding Journal in bib
\usepackage{graphics,graphicx}
%
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\mbh}{\mbox{$M_{\rm BH}$}\xspace}
\newcommand{\mdyn}{\mbox{$M_{\rm dyn}$}\xspace}
\newcommand{\mbulge}{\mbox{$M_{\rm bulge}$}\xspace}
\newcommand{\mstar}{\mbox{$M^*$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\Rsun}{\mbox{$R_{\odot}$}\xspace}
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
%
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\aco}{\mbox{CO($J$\,=\,1\,\rarr\,0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$\,=\,2\,\rarr\,1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$\,=\,3\,\rarr\,2)}\xspace}
\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}}
%
\newcommand{\cii}{[C{\scriptsize II}]}
\newcommand{\mgii}{\mbox{Mg{\scriptsize II}~2798\AA}\xspace}
\newcommand{\oiii}{\mbox{$[$O{\scriptsize III}$]$~4959, 5007\AA}\xspace}
\newcommand{\oii}{\mbox{$[$O{\scriptsize II}$]$~3727\AA}\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}\xspace}
\newcommand{\kms}{\mbox{km\,s$^{-1}$}\xspace}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\alphaco}{\mbox{$\alpha_{\rm CO}$}\xspace}
\newcommand{\alphaU}{\mbox{$M_{\odot}~($K\,\,km\,\,pc$^2)^{-1}$}\xspace}
\newcommand{\sfrU}{\mbox{\Msun\,yr$^{-1}$}\xspace}
% Numerical values
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\petm}[2]{$^{+#1}_{-#2}$}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
%
\newcommand{\eg}{{e.g.,~}}
\newcommand{\ie}{{i.e.,~}}
%
\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\Sec}[1]{\S\ref{sec:#1}}
%
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}
\newcommand\tnl{\,\tablenotemark{l}}
%
\def\herschel {{\it Herschel Space Observatory}\xspace}
\def\hst {{\it Hubble Space Telescope}\xspace}
\def\alma     {Atacama Large (sub-)Millimeter Array (ALMA)\xspace}
\def\spitzer {{\it Spitzer Space Telescope}\xspace}
\def\pdbi     {Plateau de Bure Interferometer\xspace}
\def\carma    {Combined Array for Research in Millimeter-wave Astronomy\xspace}
\def\cso      {Caltech Sumillimeter Observatory (CSO)\xspace}
\def\noema    {Northern Extended Millimeter Array (NOEMA)\xspace}
\def\vla      {{\it Karl G. Jansky} Very Large Array\xspace}
% Typography
\newcommand{\ncode}[1]{{\sc #1}}
% Codes / Softwares
\newcommand{\uvmcmcfit}{\ncode{uvmcmcfit}\xspace}
\def\aips {\ncode{AIPS}\xspace}
\def\casa {\ncode{CASA}\xspace}
% Long words
\newcommand{\obs}{observations\xspace}
\newcommand{\lowZ}{low-metallicity\xspace}
\newcommand{\mulw}{multi-wavelength\xspace}
\newcommand{\SF}{star formation\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\SBs}{starbursts\xspace}
\newcommand{\gl}{gravitationally lensed\xspace}
\newcommand{\MCMC}{Markov Chain Monte Carlo (MCMC)\xspace}
\newcommand{\ms}{``main-sequence''\xspace}
% Wavelength regimes
\newcommand{\fir}{far-IR\xspace}
\newcommand{\fuv}{far-UV\xspace}
\newcommand{\mir}{mid-IR\xspace}
\newcommand{\nir}{near-IR\xspace}

\slugcomment{To be submitted to the ApJ}
\makeatletter
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{document}

@@

@@

\section{Introduction}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
It is currently not well-understood when and how the supermassive black holes (SMBHs) and
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
but direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
spatially unresolved CO observations of
a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}.

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
\citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a},
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
\defcitealias{Claeskens06a}{C06}

\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

The \ncode{gildas} package was used to calibrate and analyze the visibility data.
The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is produced by averaging over 3.16\,GHz of line-free bandwidth. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$.

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\subsection{VLA (Archival)}
Our analysis also uses archival data of the 4.885\,GHz
radio continuum obtained with the
VLA (Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{f1.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

@@

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
